---
title: "Bridge Analysis"
author: "DX Analytics https://dxan.co.uk"
date: "`r format(Sys.time(), '%d %B %Y')`"
output: 
  html_document:
    theme: journal
    highlight: monochrome
    toc: true
    number_sections: true
    code_folding: none
    toc_depth: 3
    toc_float:
      collapsed: true
      smooth_scroll: false
---

<script>
   $(document).ready(function() {
     $head = $('#header');
     $head.prepend('<img src=\"logowhite_verysmall.png\" style=\"float: right;\"/>')
   });
</script>

```{r setup, include=FALSE}
library(ggplot2)
# set up a new base-theme for all plots 
theme_bw2<-theme_bw()+
  theme(# axis labels
             axis.title = element_text(size = 20),
             # tick labels
             axis.text = element_text(size = 20),
             # title 
             title = element_text(size = 20),
             legend.text=element_text(size=20)
             )
theme_set(theme_bw2)

knitr::opts_chunk$set(echo=FALSE, warning=FALSE, message=FALSE, fig.width=15, fig.height=9)
```

<br><br>

> Use case of bridge data analysis: Part I Interactive Data Visualisation

# Data overview
***
Data are in a nested format: 120 recorded items per bridge per state, repeated annually in 2010 - 2018. 

  * **`r length(unique(tmp$STRUCTURE_NUMBER_008))` ** structures 
  * **`r length(unique(tmp$STATE_CODE_001))` ** US states 
  * **`r nrow(tmp)` ** structure-year records processed
  
## Bridge map  

```{r}
library(leaflet)
library(geojsonio)
library(dplyr)
library(sjlabelled)

# load basic US map data
states <- geojsonio::geojson_read("https://raw.githubusercontent.com/PublicaMundi/MappingAPI/master/data/geojson/us-states.json", what = "sp")
# class(states)
# names(states)

# name = state name, density = population density, replace with bridge info.
# For continuous (cat.) variables: within each state is summed (med.) across all bridges for each year and then look at median across years.
# general condition: poor
# scour condition: % critical

a<-tmp %>% group_by(STATE_CODE_001) %>%
  mutate(n_brd=n_distinct(STRUCTURE_NUMBER_008,na.rm=T)) %>%
           ungroup() %>%
           group_by(STATE_CODE_001,Year) %>% 
           mutate(sum_cost=as.numeric(sum(TOTAL_IMP_COST_096,na.rm=T)),
                  sum_cond=as.numeric(median(as.numeric(GEN_COND.alt),na.rm=T)),
                  sum_scr=as.numeric(median(as.numeric(SCOUR_CRITICAL_113.alt),na.rm=T)),
                  sum_ADT=as.numeric(sum(ADT_029,na.rm=T)),
                  sum_tkADT=as.numeric(sum(ADT_029*PERCENT_ADT_TRUCK_109/100,na.rm=T)),
                  sum_cond_bad=as.numeric(sum(as.numeric(GEN_COND.alt)==1,na.rm=T)/n()),
                  sum_scr_bad=as.numeric(sum(as.numeric(SCOUR_CRITICAL_113.alt)==1,na.rm=T)/n())) %>%
           slice(1) %>%
           ungroup() %>%
           group_by(STATE_CODE_001) %>%
  # set labels for categorical data
           mutate(med_cost=median(sum_cost,na.rm=T)/10^6, # unit = $B
                  med_cond_bad=median(sum_cond_bad,na.rm=T)*100,
                  med_scr_bad=median(sum_scr_bad,na.rm=T)*100,
                  med_ADT=median(sum_ADT,na.rm=T)/10^6, # unit = M
                  med_tkADT=median(sum_tkADT,na.rm=T)/10^6, # unit = M
                  name=as_character(STATE_CODE_001)) %>%
           slice(1) %>% 
  ungroup()


# merge with the map data
states@data<-states@data %>%
  left_join(a %>% select(name,n_brd,med_cost,med_cond_bad,med_scr_bad,
                         med_ADT,med_tkADT),
            by="name")

# Prepare the text for tooltips - this bit is not changing by layers
mytext <- paste(
    "<strong>" , states@data$name,"</strong><br/>", 
    "Number of bridges: ", states@data$n_brd, "<br/>", 
    "Median total cost ($B): ", round(states@data$med_cost,2),"<br/>" ,
    "Median % bridges in poor general condition: ", round(states@data$med_cond_bad,1), "<br/>",
    "Median % bridges in closed/critical scour condition: ", round(states@data$med_scr_bad,1), "<br/>",
    "Median ADT (M): ", round(states@data$med_ADT,1), "<br/>",
    "Median truck ADT (M): ",round(states@data$med_tkADT,1), "<br/>",
    sep="") %>%
  lapply(htmltools::HTML)

# prepare the plots  
library(RColorBrewer)

# create a function for multiple layers (define what layers you need)
names(states@data)[-c(1:3)]<-c("Number of bridges","Total cost_Bn","pct poor general condition","pct critical scour condition","ADT_Mn","Truck ADT_Mn")
group <- c(names(states@data[,-c(1:3)]))

fill <- vector("list", length(group))
# create color pallette by group
for (i in 1:length(group)){
  fill[[i]] = colorBin(palette="YlOrBr", domain=states@data[[group[i]]], 
                       na.color="transparent", 
                       bins=sapply(seq(0,1,0.2),function(x){
                         as.numeric(quantile(as.numeric(states@data[[group[i]]]),x,na.rm=T))
                       }))
}

# Final Map

rawmap<-leaflet(states) %>% 
    # limit to US states only
    setView(-96, 37.8, 4) %>%
    addProviderTiles("MapBox", options = providerTileOptions(
    id = "mapbox.light",
    accessToken = Sys.getenv('MAPBOX_ACCESS_TOKEN'))) 


LeafletLayer <- function(map, fillColor, group){
  for (i in 1:length(group)){
  map <-map %>%
    addPolygons(
      fillColor = fill[[i]](states@data[[group[i]]]),
      weight = 2,
      opacity = 1,
      color = "white",
      dashArray = "3",
      fillOpacity = 0.9,
      stroke=T,
      group = group[i],
      
      # add highlights for mouse-over areas

      highlight = highlightOptions(
        weight = 5,
        color = "#666",
        dashArray = "",
        fillOpacity = 0.7,
        bringToFront = TRUE),
      label = mytext,
      labelOptions = labelOptions(
        style = list("font-weight" = "normal", padding = "3px 8px"),
          textsize = "13px",
          direction = "auto")) %>%
     addLegend(pal = fill[[i]], values = states@data[[group[i]]], opacity = 0.9, title = group[i],
    position = "bottomright")
  }
  map <- addLayersControl(map=map, baseGroups = group,position="bottomleft",
                          options = layersControlOptions(collapsed = FALSE)) %>%
    # make legend list interactive to user input 
    htmlwidgets::onRender("
    function(el, x) {
      var updateLegend = function () {
          var selectedGroup = document.querySelectorAll('input:checked')[0].nextSibling.innerText.substr(1);

          document.querySelectorAll('.legend').forEach(a => a.hidden=true);
          document.querySelectorAll('.legend').forEach(l => {
            if (l.children[0].children[0].innerText == selectedGroup) l.hidden=false;
          });
      };
      updateLegend();
      this.on('baselayerchange', e => updateLegend());
    }")
}

map <- LeafletLayer(map=rawmap, fillColor=fill, group=group)
map

```
  
## Number of structures

```{r}
library(dplyr)
library(scales)
library(ggplot2)
a<-tmp %>% group_by(STATE_CODE_001) %>%
  mutate(cnt=n_distinct(STRUCTURE_NUMBER_008)) %>%
  slice(1) %>%
  select(STATE_CODE_001,cnt) %>%
  ungroup() %>%
  arrange(desc(cnt))

ggplot(na.omit(a), aes(x = factor(reorder(STATE_CODE_001,-cnt)),y = cnt)) + 
  geom_bar(stat = "identity") +
  scale_y_continuous(breaks=pretty_breaks())+
  labs(x = "State\n", y = "Number of structures\n") +
  theme(axis.text.x = element_text(angle=90,vjust=0))

```

## The top 10 states with the most structures

```{r}
tmp %>% group_by(STATE_CODE_001) %>%
  mutate(cnt=n_distinct(STRUCTURE_NUMBER_008)) %>%
  slice(1) %>%
  select(STATE_CODE_001,cnt) %>%
  ungroup() %>%
  arrange(desc(cnt)) %>%
  mutate(pct=paste0(round(cnt/sum(cnt,na.rm=T),2)*100, "%")) %>%
  slice(1:10)
```

## Number of structures with repeated measurements 

* Number of bridges with data in both **2010** and **2018**

```{r}
a<-tmp %>% filter(Year %in% c(2010,2018)) %>%
  group_by(STRUCTURE_NUMBER_008) %>%
  mutate(cnt=n_distinct(Year)) %>%
  ungroup() %>%
  select(STRUCTURE_NUMBER_008,cnt) %>%
  filter(cnt==2)

paste0("Count=",length(unique(a$STRUCTURE_NUMBER_008)), " (",round(length(unique(a$STRUCTURE_NUMBER_008))/length(unique(tmp$STRUCTURE_NUMBER_008))*100,0),"%)")

```

* More details

```{r}
a<-tmp%>% group_by(STRUCTURE_NUMBER_008) %>%
  mutate(rep_years=n_distinct(Year)) %>%
  slice(1) %>%
  ungroup() %>%
  group_by(rep_years) %>%
  mutate(cnt=n_distinct(STRUCTURE_NUMBER_008)) %>%
  slice(1) %>%
  select(rep_years,cnt) %>%
  ungroup() %>%
  arrange(desc(cnt))

ggplot(na.omit(a), aes(x = factor(reorder(rep_years,-cnt)),y = cnt/sum(cnt)*100)) + 
  geom_bar(stat = "identity") +
  scale_y_continuous(breaks=pretty_breaks())+
  labs(x = "Repeated years\n", y = "% structures\n") +
  geom_text(aes(label=round(cnt/sum(cnt)*100,0)))+
  theme(axis.text.x = element_text(angle=90,vjust=0))
  
```

# Outcomes
***
## Cost {.tabset .tabset-pills .tabset-fade}

  * Dropdown menu to select **Bridge/Roadway/Total** cost
  * Sum across all bridges within each state for each year
  * One data point = one state-year record

### All states {.unlisted .unnumbered}

```{r}
library(stringr)
library(bsselectR)
state_plots <- paste0(list.files("outputs/cost", full.names = TRUE))
names(state_plots) <- str_replace_all(state_plots, 
                                      c("\\.png" = "", 
                                        "outputs/cost/" = ""))

bsselect(state_plots, type = "img", selected = "BRIDGE_IMP_COST_094", 
         live_search = TRUE, show_tick = TRUE, width=15, height=20)
```

### Select states: highly variable annual cost {.unlisted .unnumbered}

  * List of such states is selected by the year-by-year cost variation. 
  * Variation = inter-quartile-range (IQR) of natural cost scale (summed over all bridges) across years.
  * Cost trajectory is plotted using a log10-scale of the **total** cost for the select states. 
  * Solid triangle = median across these 10 selected states.
  
```{r}
library(stringr)
library(bsselectR)
state_plots <- paste0(list.files("outputs/cost_slt", full.names = TRUE))
names(state_plots) <- str_replace_all(state_plots, 
                                      c("\\.png" = "", 
                                        "outputs/cost_slt/" = ""))

bsselect(state_plots, type = "img", selected = "BRIDGE_IMP_COST_094.slt", 
         live_search = TRUE, show_tick = TRUE, width=15, height=20)
```

### All states: by general condition {.unlisted .unnumbered}

  * General condition computed as the minimum of deck, superstructure, substructure, culverts condition (items 58, 59, 60, 62).
  * Grouped into Poor (<=4), Fair (5-6), Good (>=7)
  * Cost trajectory is plotted using a log10-scale of the **median** cost of all structures across all states in each condition bucket.
  * Solid triangle = median across all conditions.
  
```{r}
library(stringr)
library(bsselectR)
state_plots <- paste0(list.files("outputs/cost2", full.names = TRUE))
names(state_plots) <- str_replace_all(state_plots, 
                                      c("\\.png" = "", 
                                        "outputs/cost2/" = ""))

bsselect(state_plots, type = "img", selected = "BRIDGE_IMP_COST_094.cond", 
         live_search = TRUE, show_tick = TRUE, width=15, height=20)
```

### All states: by scour condition {.unlisted .unnumbered}

  * Grouped code: 0-3 (Closed/critical), 4-7,U (Stable), 8-9,T (Good). 
  * NA = not recorded 
  * Cost trajectory is plotted using a log10-scale of the **median** cost of all structures across all states in each condition bucket.
  * Solid triangle = median across all scour conditions.
  
```{r}
library(stringr)
library(bsselectR)
state_plots <- paste0(list.files("outputs/cost3", full.names = TRUE))
names(state_plots) <- str_replace_all(state_plots, 
                                      c("\\.png" = "", 
                                        "outputs/cost3/" = ""))

bsselect(state_plots, type = "img", selected = "BRIDGE_IMP_COST_094.scour", 
         live_search = TRUE, show_tick = TRUE, width=15, height=20)
```

## Condition: General {.tabset .tabset-pills .tabset-fade}
  
  * Original codes = 0 (bad) - 9 (excellent)
  * Grouped codes: Poor (0-4), Fair (5-6), Good (7-9)
  * General condition is computed as the minimum of deck, superstructure, substructure, culverts condition (items 58, 59, 60, 62). Grouped into Poor (<=4), Fair (5-6), Good (>=7)
  * Y-axis = percentage of structures across all states in each year (stratified by respective condition)
  * Unless otherwise stated, NA = not recorded/not applicable
  * Dropdown menu to select states
  
### General {.unlisted .unnumbered}
```{r}
library(stringr)
library(bsselectR)
state_plots <- paste0(list.files("outputs/cond_gen", full.names = TRUE))
names(state_plots) <- str_replace_all(state_plots, 
                                      c("\\.png" = "", 
                                        "outputs/cond_gen/" = ""))

bsselect(state_plots, type = "img", selected = "Alabama", 
         live_search = TRUE, show_tick = TRUE, width=15, height=20)
```
  
  
### DECK {.unlisted .unnumbered}
```{r}
library(stringr)
library(bsselectR)
state_plots <- paste0(list.files("outputs/cond_deck", full.names = TRUE))
names(state_plots) <- str_replace_all(state_plots, 
                                      c("\\.png" = "", 
                                        "outputs/cond_deck/" = ""))

bsselect(state_plots, type = "img", selected = "Alabama", 
         live_search = TRUE, show_tick = TRUE, width=15, height=20)
```

### Superstructure {.unlisted .unnumbered}

```{r}
library(stringr)
library(bsselectR)
state_plots <- paste0(list.files("outputs/cond_sup", full.names = TRUE))
names(state_plots) <- str_replace_all(state_plots, 
                                      c("\\.png" = "", 
                                        "outputs/cond_sup/" = ""))

bsselect(state_plots, type = "img", selected = "Alabama", 
         live_search = TRUE, show_tick = TRUE, width=15, height=20)
```

### Substructure {.unlisted .unnumbered}

```{r}
library(stringr)
library(bsselectR)
state_plots <- paste0(list.files("outputs/cond_sub", full.names = TRUE))
names(state_plots) <- str_replace_all(state_plots, 
                                      c("\\.png" = "", 
                                        "outputs/cond_sub/" = ""))

bsselect(state_plots, type = "img", selected = "Alabama", 
         live_search = TRUE, show_tick = TRUE, width=15, height=20)
```

### Channel {.unlisted .unnumbered}

```{r}
library(stringr)
library(bsselectR)
state_plots <- paste0(list.files("outputs/cond_chnl", full.names = TRUE))
names(state_plots) <- str_replace_all(state_plots, 
                                      c("\\.png" = "", 
                                        "outputs/cond_chnl/" = ""))

bsselect(state_plots, type = "img", selected = "Alabama", 
         live_search = TRUE, show_tick = TRUE, width=15, height=20)
```

### Culvert {.unlisted .unnumbered}

```{r}
library(stringr)
library(bsselectR)
state_plots <- paste0(list.files("outputs/cond_culv", full.names = TRUE))
names(state_plots) <- str_replace_all(state_plots, 
                                      c("\\.png" = "", 
                                        "outputs/cond_culv/" = ""))

bsselect(state_plots, type = "img", selected = "Alabama", 
         live_search = TRUE, show_tick = TRUE, width=15, height=20)
```

## Condition: Scour

* Original code: 0 (structure closed) - 9 (excellent condition), N, T, U
* Grouped code: 0-3 (Closed/critical), 4-7,U (Stable), 8-9,T (Good). NA = not recorded/not applicable
* Code N: no waterway (will be excluded in the following plots)
* Code T: tidal water cannot be inspected (manual states low risk) 
* Dropdown menu to select states

```{r}
library(stringr)
library(bsselectR)
state_plots <- paste0(list.files("outputs/cond_scour", full.names = TRUE))
names(state_plots) <- str_replace_all(state_plots, 
                                      c("\\.png" = "", 
                                        "outputs/cond_scour/" = ""))

bsselect(state_plots, type = "img", selected = "Alabama", 
         live_search = TRUE, show_tick = TRUE, width=15, height=20)
```

## Evaluation: Detour {.tabset .tabset-pills .tabset-fade}

  * Detour is evaluated in kilometers
  * Solid triangle = median across all conditions
  * Dropdown menu to select states
  
### All states {.unlisted .unnumbered}

```{r}
  a<-tmp %>%
    group_by(STATE_CODE_001,Year) %>%  
    # s is the median for all bridges
    mutate(s=as.numeric(median(DETOUR_KILOS_019,na.rm=T))) %>%
    distinct(STATE_CODE_001,Year,.keep_all = T) %>%
    ungroup()
  
  p<-ggplot(a, aes(x = factor(reorder(STATE_CODE_001,-NUM_BY_STATE)),y = s)) + 
    geom_jitter(color="grey")+
    geom_boxplot() +
    scale_y_continuous(breaks=pretty_breaks())+
    labs(x = "State (ordered by the number of bridges, from highest to lowest) \n", 
         y = paste0(label(tmp$DETOUR_KILOS_019),", median across all bridges"))+
    theme(axis.text.x = element_text(angle=90,vjust=0))
  p
```

### Select states: highly variable detour by year {.unlisted .unnumbered}

```{r}
  a<-tmp %>%
    group_by(STATE_CODE_001,Year) %>%  
    # s is the median for all bridges
    mutate(s=as.numeric(median(DETOUR_KILOS_019,na.rm=T))) %>%
    distinct(STATE_CODE_001,Year,.keep_all = T) %>%
    ungroup()
  
  b<-a %>% group_by(STATE_CODE_001) %>% mutate(variation=IQR(s,na.rm=T)) %>%
    distinct(STATE_CODE_001,variation) %>%
    ungroup() %>%
    arrange(desc(variation)) %>%
    top_n(10)
  
  p<-ggplot(a %>% filter(STATE_CODE_001 %in% b$STATE_CODE_001), aes(x = factor(Year),y = s, group=STATE_CODE_001,colour=STATE_CODE_001)) + 
    geom_line()+
    stat_summary(
      aes(group=1),
      geom="point",
      fun.y = median,
      shape=17, size=3)+
    scale_y_continuous(breaks=pretty_breaks())+
    labs(x = "Year\n", y = paste0(label(tmp$DETOUR_KILOS_019),", median across all bridges"))+
    theme(axis.text.x = element_text(angle=90,vjust=0))
  p
```

### All states: by general condition {.unlisted .unnumbered}

```{r}
library(stringr)
library(bsselectR)
state_plots <- paste0(list.files("outputs/eval_detour2", full.names = TRUE))
names(state_plots) <- str_replace_all(state_plots, 
                                      c("\\.png" = "", 
                                        "outputs/eval_detour2/" = ""))

bsselect(state_plots, type = "img", selected = "Alabama", 
         live_search = TRUE, show_tick = TRUE, width=15, height=20)
```

### All states: by scour condition {.unlisted .unnumbered}

```{r}
library(stringr)
library(bsselectR)
state_plots <- paste0(list.files("outputs/eval_detour3", full.names = TRUE))
names(state_plots) <- str_replace_all(state_plots, 
                                      c("\\.png" = "", 
                                        "outputs/eval_detour3/" = ""))

bsselect(state_plots, type = "img", selected = "Alabama", 
         live_search = TRUE, show_tick = TRUE, width=15, height=20)
```

## Evaluation: Traffic 
  
  * Average daily traffic (ADT), recoded in millions (M)
  * All plots by **general** or **scour** condition
  * Dropdown menu to select states
  
### By general condition {.tabset .tabset-pills .tabset-fade}  
  
#### ADT (current) {.unlisted .unnumbered}
  
  * Current = at the year of inspection
  * Plotted **total** ADT across all bridges

```{r}
library(stringr)
library(bsselectR)
state_plots <- paste0(list.files("outputs/eval_tfc_adt_gen", full.names = TRUE))
names(state_plots) <- str_replace_all(state_plots, 
                                      c("\\.png" = "", 
                                        "outputs/eval_tfc_adt_gen/" = ""))

bsselect(state_plots, type = "img", selected = "Alabama", 
         live_search = TRUE, show_tick = TRUE, width=15, height=20)
```

#### ADT-truck (current, in %) {.unlisted .unnumbered}
  * Current = current percentage of the average daily traffic that is truck traffic
  * Measured at the year of inspection
  * Plotted **median** across all bridges 

```{r}
library(stringr)
library(bsselectR)
state_plots <- paste0(list.files("outputs/eval_tfc_trk_gen", full.names = TRUE))
names(state_plots) <- str_replace_all(state_plots, 
                                      c("\\.png" = "", 
                                        "outputs/eval_tfc_trk_gen/" = ""))

bsselect(state_plots, type = "img", selected = "Alabama", 
         live_search = TRUE, show_tick = TRUE, width=15, height=20)
```

#### ADT (future) {.unlisted .unnumbered}
  * Estimated future average daily traffic (a basis for 20-year forecast)
  * Plotted **total** across all bridges 

```{r}
library(stringr)
library(bsselectR)
state_plots <- paste0(list.files("outputs/eval_tfc_ftr_gen", full.names = TRUE))
names(state_plots) <- str_replace_all(state_plots, 
                                      c("\\.png" = "", 
                                        "outputs/eval_tfc_ftr_gen/" = ""))

bsselect(state_plots, type = "img", selected = "Alabama", 
         live_search = TRUE, show_tick = TRUE, width=15, height=20)
```

### By scour condition {.tabset .tabset-pills .tabset-fade}  

#### ADT (current) {.unlisted .unnumbered}
  
  * Current = at the year of inspection
  * Plotted **total** ADT across all bridges

```{r}
library(stringr)
library(bsselectR)
state_plots <- paste0(list.files("outputs/eval_tfc_adt_scour", full.names = TRUE))
names(state_plots) <- str_replace_all(state_plots, 
                                      c("\\.png" = "", 
                                        "outputs/eval_tfc_adt_scour/" = ""))

bsselect(state_plots, type = "img", selected = "Alabama", 
         live_search = TRUE, show_tick = TRUE, width=15, height=20)
```

#### ADT-truck (current, in %) {.unlisted .unnumbered}
  * Current = current percentage of the average daily traffic that is truck traffic
  * Measured at the year of inspection
  * Plotted **median** across all bridges 

```{r}
library(stringr)
library(bsselectR)
state_plots <- paste0(list.files("outputs/eval_tfc_trk_scour", full.names = TRUE))
names(state_plots) <- str_replace_all(state_plots, 
                                      c("\\.png" = "", 
                                        "outputs/eval_tfc_trk_scour/" = ""))

bsselect(state_plots, type = "img", selected = "Alabama", 
         live_search = TRUE, show_tick = TRUE, width=15, height=20)
```

#### ADT (future) {.unlisted .unnumbered}
  * Estimated future average daily traffic (a basis for 20-year forecast)
  * Plotted **total** across all bridges 

```{r}
library(stringr)
library(bsselectR)
state_plots <- paste0(list.files("outputs/eval_tfc_ftr_scour", full.names = TRUE))
names(state_plots) <- str_replace_all(state_plots, 
                                      c("\\.png" = "", 
                                        "outputs/eval_tfc_ftr_scour/" = ""))

bsselect(state_plots, type = "img", selected = "Alabama", 
         live_search = TRUE, show_tick = TRUE, width=15, height=20)
```

# Relationship between outcomes
***
Outcomes of interest are:

  1. Cost (continuous)
  
    * Bridge, Roadway, Total improvement cost estimates
    
  2. Condition (categorical)
  
    * General
    * Scour
  
  3. Evaluation_Detour (continuous)
  
  4. Evaluation_Traffic (continuous)
  
    * ADT_current, ADT_truck, ADT_future
    
Correlation plots:   

  * Dropdown menu to select states 
  * Correlations are plotted for bridges with median annual values in 2010-2018
  * States with co-linear outcomes are not shown (potential data recording error)
  * Edge = correlation, Green = positive, Red = negative
  * Non-signficant edges, with p-value (Bonferroni-corrected) > 0.05. are removed  
  
```{r}
library(stringr)
library(bsselectR)

state_plots <- paste0(list.files("outputs/corr_ep", full.names = TRUE))
names(state_plots) <- str_replace_all(state_plots, 
                                      c("\\.png" = "", 
                                        "outputs/corr_ep/" = ""))

bsselect(state_plots, type = "img", selected = "Alabama", 
         live_search = TRUE, show_tick = TRUE, width=15, height=20)
```

# Relationship between predictors
***

* Distributions are summarised in a downloadable spreadsheet.
* Summaries for year 2018 are reported. 20 bridges are randomly selected in each state.
* Summaries are separated by general condition, with p-values<0.05 indicating statistically significant relationship between predictor and condition.

```{r}
library(table1)
library(DT)
library(htmltab)
library(arsenal)

# Create table with these indices to be excluded as columns
index<-c(2:21,24,26,28,29,32,41,46,47,49,67,68,69,70,71,76,77,78,79,80,81,82,85,87,88,89,107,115,96,147,148,
         25,31,45,51,74,86,90,91,92,96,97,98,99,103,105,113,114,117)

a<-tmp[tmp$Year==2018,-index] %>%
  group_by(STATE_CODE_001) %>%
  sample_n(20) %>%
  ungroup() %>%
  select(-STATE_CODE_001)

# # randomly sample x columns
# x<-5
# index<-c(sample(ncol(a),x),ncol(a))
  
mycontrols  <- tableby.control(test=T, total=T,digits = 1, digits.pct = 1,digits.p=3,
                               numeric.test="kwt", cat.test="chisq")

datatable(data = as.data.frame(summary(
  tableby(GEN_COND.alt~., data=a,control=mycontrols),
  text=T)),
          extensions = list('Buttons' = NULL, 'FixedColumns' = NULL),
          rownames = FALSE,
      options = list(
        paging=TRUE,
        ordering=FALSE,
       dom = 'Bfrtip',
      scrollX = TRUE,
      pageLength = 15,
      fixedHeader = TRUE,
      fixedColumns = list(leftColumns = 1)))

```
  